WASP-4\lowercase{b} Arrived Early for the TESS Mission

### 2019-02-24 paper/ms.tex
minor paper updates

@@

\added{We fit each model by assuming a Gaussian likelihood and sampling over 
the posterior probability distributions.}
Figure~\ref{fig:times} shows the residuals with respect to the
constant-period model.  The best-fitting constant-period model has
$\chi^2 = 174$ and 61 degrees of freedom.  The best-fitting
decreasing-period model has $\chi^2 = 62.6$ and 60 degrees of freedom.
The best-fitting precession model has $\chi^2 = 64.3$ and 58 degrees
of freedom.  Either of the latter two models provides a much better
fit than the constant-period model.  The difference in $\chi^2$
between the first and second models corresponds to $p \approx
10^{-26}$.

The decreasing-period model provides a slightly better fit to the data
than the precession model.  It is favored by $\Delta \chi^2 = 1.7$,
and has two fewer free parameters.  A useful heuristic for model
comparison is the Bayesian Information Criterion (BIC),
\begin{equation}
  {\rm BIC} = \chi^2 + k\log n,
\end{equation}
where $k$ is the number of free parameters, and $n$ is the number of
data points. In this case, $n=62$.  The difference in the BIC between
the precession and decay models is $\Delta {\rm BIC} = {\rm BIC}_{\rm
  prec} - {\rm BIC}_{\rm quad} = 10$, corresponding to a Bayes factor
of $1.1\times 10^{4}$.  Likewise, the Akaike Information Criterion
favors the constant-period-derivative model by $\Delta {\rm AIC} =
5.8$.  Differences of this magnitude are traditionally deemed ``strong
evidence'' that one model is a better description of the data than the
other \citep{kass_bayes_1995}, although we prefer to reserve judgment
until more data can be obtained.

In the decreasing-period model, the period derivative is
\begin{equation}
\dot{P}
  = - (4.00 \pm 0.38)\times 10^{-10}
  = - 12.6 \pm 1.2~{\rm ms}\,{\rm yr}^{-1}.
  \label{eq:dP_dt_obs}
\end{equation}
For comparison, the best-fitting period derivative of WASP-12b is
$\dot{P} = -29 \pm 3\,{\rm ms}\,{\rm yr}^{-1}$
\citep{maciejewski_departure_2016,patra_2017}.  If both planets are
truly falling onto their stars, then WASP-4b is falling at about half
the rate of WASP-12b.  In the precession model, the best-fit
eccentricity is
\begin{equation}
  e = (1.92^{+ 1.93}_{- 0.76})\times10^{-3}
\end{equation}
The longitude of periastron advances by $\dot{\omega} =
13.6^{+4.7}_{-3.6}\ {\rm degrees}\,{\rm yr}^{-1}$, and the precession
period is $27^{+10}_{-7}$ years.  All of the best-fitting parameters
(the medians of the posterior distributions) and the 68\% credible
intervals are reported in Table~4.

@@

\acknowledgements
L.G.B.\ and J.N.W.\ gladly acknowledge helpful discussions with
A.~Bailey, F.~Dai, J.~Goodman, K.~Patra and V.~Van Eylen, and are
grateful to the people who have turned TESS from an idea into reality.
%
WASP-4 was included on the ``short-cadence'' target list thanks to the
Guest Investigator programs of J.\ Southworth and S.\ Kane (G011112
and G011183 respectively). 
%
J.N.W.\ thanks the TESS project and the Heising-Simons foundation for
supporting this work.
%
J.M.D. acknowledges funding from the European Research Council (ERC)
under the European Union's Horizon 2020 research and innovation
programme (grant agreement no. 679633; Exo-Atmos), and support from
the NWO TOP Grant Module 2 (Project Number 614.001.601).
%
J.E.R. was supported by the Harvard Future Faculty Leaders
Postdoctoral fellowship.
%
This paper includes data collected by the TESS mission, which are
publicly available from the Mikulski Archive for Space Telescopes
(MAST).
%
Funding for the TESS mission is provided by NASA's Science Mission
directorate.
%
This research has made use of the NASA Exoplanet Archive, which is
operated by the California Institute of Technology, under contract
with the National Aeronautics and Space Administration under the
Exoplanet Exploration Program.
%
This work made use of NASA's Astrophysics Data System Bibliographic
Services.
%
This research has made use of the VizieR catalogue access tool, CDS,
Strasbourg, France. The original description of the VizieR service was
published in A\&AS 143, 23.
%
This work has made use of data from the European Space Agency (ESA)
mission {\it Gaia} (\url{https://www.cosmos.esa.int/gaia}), processed
by the {\it Gaia} Data Processing and Analysis Consortium (DPAC,
\url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding
for the DPAC has been provided by national institutions, in particular
the institutions participating in the {\it Gaia} Multilateral
Agreement.
%
\newline
%
\facility{
	TESS \citep{ricker_transiting_2015},
	Gaia \citep{gaia_collaboration_gaia_2016,gaia_collaboration_gaia_2018}
}
%
\software{
  \texttt{astrobase} \citep{bhatti_astrobase_2018},
  \texttt{astropy} \citep{the_astropy_collaboration_astropy_2018},
  \texttt{astroquery} \citep{astroquery_2018},
  \texttt{BATMAN} \citep{kreidberg_batman_2015},
  \texttt{corner} \citep{corner_2016},
  \texttt{emcee} \citep{foreman-mackey_emcee_2013},
  \texttt{IPython} \citep{perez_2007},
  \texttt{matplotlib} \citep{hunter_matplotlib_2007}, 
  \texttt{MESA} 
  \citep{paxton_modules_2011,paxton_modules_2013,paxton_modules_2015}
  \texttt{numpy} \citep{walt_numpy_2011}, 
  \texttt{pandas} \citep{mckinney-proc-scipy-2010},
  \texttt{scikit-learn} \citep{scikit-learn},
  \texttt{scipy} \citep{jones_scipy_2001}.
}

>>>>

\author[0000-0002-8958-0683]{F. Dai}

@@

\added{We fit each model by assuming a Gaussian likelihood and sampling over 
the posterior probability distributions. The prior for the quadratic
model allowed the period derivative to have any sign.}
Figure~\ref{fig:times} shows the residuals with respect to the
constant-period model.  The best-fitting constant-period model has
$\chi^2 = 174$ and 61 degrees of freedom.  The best-fitting
\replaced{decreasing-period}{quadratic} model has $\chi^2 = 62.6$ and 60 degrees of freedom.
The best-fitting precession model has $\chi^2 = 64.3$ and 58 degrees
of freedom.  Either of the latter two models provides a much better
fit than the constant-period model.  The difference in $\chi^2$
between the first and second models corresponds to $p \approx
10^{-26}$.

The \replaced{decreasing-period}{quadratic} model provides a slightly better fit to the data
than the precession model.  It is favored by $\Delta \chi^2 = 1.7$,
and has two fewer free parameters.  A useful heuristic for model
comparison is the Bayesian Information Criterion (BIC),
\begin{equation}
  {\rm BIC} = \chi^2 + k\log n,
\end{equation}
where $k$ is the number of free parameters, and $n$ is the number of
data points. In this case, $n=62$.  The difference in the BIC between
the precession and decay models is $\Delta {\rm BIC} = {\rm BIC}_{\rm
  prec} - {\rm BIC}_{\rm quad} = 10$, corresponding to a Bayes factor
of $1.1\times 10^{4}$.  Likewise, the Akaike Information Criterion
favors the constant-period-derivative model by $\Delta {\rm AIC} =
5.8$.  Differences of this magnitude are traditionally deemed ``strong
evidence'' that one model is a better description of the data than the
other \citep{kass_bayes_1995}, although we prefer to reserve judgment
until more data can be obtained.

In the \replaced{decreasing-period}{quadratic} model, the period derivative is
\begin{equation}
\dot{P}
  = - (4.00 \pm 0.38)\times 10^{-10}
  = - 12.6 \pm 1.2~{\rm ms}\,{\rm yr}^{-1}.
  \label{eq:dP_dt_obs}
\end{equation}
For comparison, the best-fitting period derivative of WASP-12b is
$\dot{P} = -29 \pm 3\,{\rm ms}\,{\rm yr}^{-1}$
\citep{maciejewski_departure_2016,patra_2017}.  If both planets are
truly falling onto their stars, then WASP-4b is falling at about half
the rate of WASP-12b.  In the precession model, the best-fit
eccentricity is
\begin{equation}
  e = (1.92^{+ 1.93}_{- 0.76})\times10^{-3}
\end{equation}
The longitude of periastron advances by $\dot{\omega} =
13.6^{+4.7}_{-3.6}\ {\rm degrees}\,{\rm yr}^{-1}$, and the precession
period is $27^{+10}_{-7}$ years.  All of the best-fitting parameters
(the medians of the posterior distributions) and the 68\% credible
intervals are reported in Table~4.

@@

\acknowledgements
L.G.B.\ and J.N.W.\ gladly acknowledge helpful discussions with
A.~Bailey, F.~Dai, J.~Goodman, K.~Patra and V.~Van Eylen, and are
grateful to the people who have turned TESS from an idea into reality.
\added{L.G.B. thanks A.~Bixel and E.~May for clarifying details
concerning the available IMACS lightcurves.}
%
WASP-4 was included on the ``short-cadence'' target list thanks to the
Guest Investigator programs of J.\ Southworth and S.\ Kane (G011112
and G011183 respectively). 
%
J.N.W.\ thanks the TESS project and the Heising-Simons foundation for
supporting this work.
%
J.M.D. acknowledges funding from the European Research Council (ERC)
under the European Union's Horizon 2020 research and innovation
programme (grant agreement no. 679633; Exo-Atmos), and support from
the NWO TOP Grant Module 2 (Project Number 614.001.601).
%
J.E.R. was supported by the Harvard Future Faculty Leaders
Postdoctoral fellowship.
%
This paper includes data collected by the TESS mission, which are
publicly available from the Mikulski Archive for Space Telescopes
(MAST).
%
Funding for the TESS mission is provided by NASA's Science Mission
directorate.
%
This research has made use of the NASA Exoplanet Archive, which is
operated by the California Institute of Technology, under contract
with the National Aeronautics and Space Administration under the
Exoplanet Exploration Program.
%
This work made use of NASA's Astrophysics Data System Bibliographic
Services.
%
This research has made use of the VizieR catalogue access tool, CDS,
Strasbourg, France. The original description of the VizieR service was
published in A\&AS 143, 23.
%
This work has made use of data from the European Space Agency (ESA)
mission {\it Gaia} (\url{https://www.cosmos.esa.int/gaia}), processed
by the {\it Gaia} Data Processing and Analysis Consortium (DPAC,
\url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding
for the DPAC has been provided by national institutions, in particular
the institutions participating in the {\it Gaia} Multilateral
Agreement.
%
\newline
%
\facility{
	TESS \citep{ricker_transiting_2015},
	Gaia \citep{gaia_collaboration_gaia_2016,gaia_collaboration_gaia_2018}
}
%
\software{
  \texttt{astrobase} \citep{bhatti_astrobase_2018},
  \texttt{astropy} \citep{the_astropy_collaboration_astropy_2018},
  \texttt{astroquery} \citep{astroquery_2018},
  \texttt{BATMAN} \citep{kreidberg_batman_2015},
  \texttt{corner} \citep{corner_2016},
  \texttt{emcee} \citep{foreman-mackey_emcee_2013},
  \texttt{IPython} \citep{perez_2007},
  \texttt{matplotlib} \citep{hunter_matplotlib_2007}, 
  \texttt{MESA} 
  \citep{paxton_modules_2011,paxton_modules_2013,paxton_modules_2015}
  \texttt{numpy} \citep{walt_numpy_2011}, 
  \texttt{pandas} \citep{mckinney-proc-scipy-2010},
  \texttt{scikit-learn} \citep{scikit-learn},
  \texttt{scipy} \citep{jones_scipy_2001}.
}
